Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2022-10-31 analysis/paper/paper.Rmd
Include figures to include captions
Fix caption breaking across pages and standardise template names

---
title: "Openness and computational reproducibility in plant pathology: where we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: ARS
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - ARS: Horticultural Crops Disease and Pest Management Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath_template.docx"
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl"
---

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  out.width = "100%",
  comment = "#>",
  dev = "cairo_ps",
  cache = FALSE
)

@@

```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
journal <-
  tabyl(rrpp, journal, year) %>%
  rowwise() %>%
  mutate(n = sum(c_across(where(is.numeric)), na.rm = T))

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>%
  rename(Journal = journal,
         `IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  fontsize(size = 10, part = "body") %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  set_caption(
    "Journal titles selected for inclusion representing 21 plant pathology journals or specialized journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated."
  )
```

>>>>

---
title: "Openness and computational reproducibility in plant pathology: where we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: ARS
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - ARS: Horticultural Crops Disease and Pest Management Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath-template.docx"
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl"
---

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  out.width = "100%",
  comment = "#>",
  dev = "cairo_ps",
  cache = FALSE,
  ft.keepnext = FALSE
)

@@

```{r journals, echo=FALSE, message=FALSE, warning=FALSE}
journal <-
  tabyl(rrpp, journal, year) %>%
  rowwise() %>%
  mutate(n = sum(c_across(where(is.numeric)), na.rm = TRUE))

distinct(rrpp, journal, IF_5year) %>%
  left_join(journal, by = "journal") %>%
  rename(Journal = journal,
         `IF` = IF_5year) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  fontsize(size = 10, part = "body") %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  set_caption("Journal titles selected for inclusion representing 21 plant pathology journals or specialized journals featuring plant pathology focused articles, their respective five-year impact factors as of 2022 (5 Year IF), number of articles per year and the total number (n) of articles from each journal that were evaluated.")
```
